A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-25 paper/fascd.tex
Some centering, some acknowledging Lawrence

\title{A full approximation scheme multilevel method \\ for nonlinear variational inequalities\thanks{Submitted to the editors DATE.
\funding{EB was supported by a Faculty Development Travel Award from United Academics, University of Alaska Fairbanks. PEF was supported by the Engineering and Physical Sciences Research Council [EPSRC grants EP/R029423/1 and EP/W026163/1]. This work used the ARCHER2 UK National Supercomputing Service (https://www.archer2.ac.uk). PEF thanks Jack D.~Betteridge for assistance with the numerical experiments of Example \ref{ex:results:sia}.}}}

@@

\begin{figure}[ht]
\includegraphics[width=0.6\textwidth]{genfigs/cartoon.pdf}
\caption{A constraint decomposition (CD) for a unilateral obstacle problem on a two-point space $\Omega=\{x_1,x_2\}$, with $\mathcal{V}=\left\{v \,:\, \Omega \to \RR\right\}$ and $\mathcal{K}=\{v\ge \psi\}$.}
\label{fig:cartoon}
\end{figure}

@@

\begin{table}[H]
\begin{tabular}{llc}
\toprule
\emph{name}  & \emph{action}  & \emph{linear?} \\ \midrule
canonical prolongation        & $P:\mathcal{V}^{j-1}\to\mathcal{V}^j$ & \,\checkmark \\
canonical (dual) restriction  & $R:(\mathcal{V}^j)'\to(\mathcal{V}^{j-1})'$ & \,\checkmark \\
(nodal) injection             & $\iR:\mathcal{V}^j\to\mathcal{V}^{j-1}$ & \,\checkmark \\
maximum injection           & $\maxR:\tilde{\mathcal{V}}^j\to\tilde{\mathcal{V}}^{j-1}$ & \ding{55} \\
minimum injection           & $\minR:\tilde{\mathcal{V}}^j\to\tilde{\mathcal{V}}^{j-1}$ & \ding{55} \\
\bottomrule
\end{tabular}
\caption{Transfer operators used in this paper.}
\label{tab:transfers}
\end{table}

@@

\begin{figure}[ht]
\input{tikz/Rplusminus.tex}
\caption{The monotone injection operators $\maxR$ and $\minR$ assign to a coarse degree of freedom (blue) the maximum and minimum respectively of the fine function over the patch of coarse cells sharing its vertex. The coarse mesh is in black and the fine in grey.}
\label{fig:Rplusminus}
\end{figure}

@@

\begin{figure}[ht]
\begin{tabular}{cc}
\input{tikz/directRbadfine.tex}
&
\input{tikz/directRbadcoarse.tex}
\end{tabular}
\caption{For the finer-level constraints $\underline{\gamma}^1$ (blue) and $\overline{\gamma}^1$ (red) on the left, direct application of $\iR,\minR,\maxR$ is problematic.  For example, if we apply the monotone injections then the resulting coarser-level constraint set $\mathcal{K}^0$ is empty because $\maxR \underline{\gamma}^1 > \minR \overline{\gamma}^1$ (right).  Defect constraints avoid this difficulty.}
\label{fig:directRbad}
\end{figure}

@@

%REGENERATE using https://github.com/bueler/mg-glaciers:
%$ cd mg-glaciers/py/
%$ [modify decomposition() inside visualize.py to turn off axes and print \gamma for obstacle]
%$ ./obstacle.py -J 5 -jcoarse 1 -random -randommodes 8 -diagnostics -o defect.pdf
%fine level 5 (m=63): using 20 V(1,0) cycles -> 38.750 WU
\begin{figure}[ht]
\includegraphics[width=0.65\textwidth]{fixfigs/chiphilevels.pdf}
\caption{Unilateral LDCs $\underline{\chi}^j$ are generated from $\underline{\chi}^J = \underline{\gamma}^J - w^J$ using maximum injection: $\underline{\chi}^j = \maxR \underline{\chi}^{j+1}$.}
\label{fig:chiphilevels}
\end{figure}

@@

\begin{figure}[ht]
\begin{center}
\input{tikz/vcycle.tex}
\end{center}
\caption{The FASCD V-cycle computes downward corrections $y_j \in \mathcal{D}^j$, but the upward corrections $z_j\in\mathcal{U}^j$ are in larger sets.}
\label{fig:fascdvcycle}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\input{tikz/fcycle.tex}
\end{center}
\caption{F-cycle Algorithm \ref{alg:fascd-fcycle} initially restricts and injects the data $\ell^J,\underline{\gamma}^J,\overline{\gamma}^J$ down to level $j=0$ (gray).  Then it prolongs and truncates (doubled edges) to create an admissible initial iterate on the next-finer level.  Solution on each level is by V-cycles. See Figure \ref{fig:fascdvcycle} for the other symbols.}
\label{fig:fcycle}
\end{figure}

@@

%REGENERATE using git@bitbucket.org:pefarrell/fascd.git, in examples/
%$ python3 drape.py -prob ball -levs 9 -o ball -fascd_rtol 1.0e-6 -fascd_atol 1.0e-6 -fascd_cycle_type full
%$ mpiexec -n 16 python3 drape.py -prob spiral -levs 10 -o spiral.pvd -fascd_levels_snes_converged_reason -fascd_rtol 1.0e-6 -fascd_atol 1.0e-6 -fascd_cycle_type full
%$ paraview ball|spiral.pvd
%use preset "xray" and invert colors; for spiral.pvd, show lgap = u - lb as black if above 0.02; for ball i used 0.001
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.35\textwidth]{fixfigs/ball-set.png} \qquad \includegraphics[width=0.35\textwidth]{fixfigs/spiral-set.png}
\end{center}
\caption{Coincidence sets for the ball and spiral problems in Example \ref{ex:results:classical}.}
\label{fig:results:classical}
\end{figure}

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py
% and https://github.com/bueler/mcd-extended: paper/results/drape.sh|txt
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\toprule
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &          & V-cycle & F-cycle & RS only & V-cycle & F-cycle & RS only \\
\midrule
 1 &    $5^2$ &  1 &  1 &  1  &  1 &  1 &  1 \\
 2 &    $9^2$ &  2 &  1 &  2  &  2 &  1 &  2 \\
 3 &   $17^2$ &  2 &  2 &  3  &  3 &  2 &  4 \\
 4 &   $33^2$ &  3 &  2 &  6  &  3 &  2 &  7 \\
 5 &   $65^2$ &  3 &  2 &  8  &  4 &  3 &  9 \\
 6 &  $129^2$ &  4 &  2 & 17  &  4 &  3 & 16 \\
 7 &  $257^2$ &  4 &  2 & 33  &  4 &  3 & 27 \\
 8 &  $513^2$ &  5 &  2 & 65  &  5 &  3 & 48 \\
 9 & $1025^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
10 & $2049^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for FASCD V-cycle and F-cycle algorithms in Example \ref{ex:results:classical}.  Smoother-only runs marked \XX\xspace were not attempted.}
\label{tab:results:classical}
\end{table}

@@

%REGENERATE using elbueler/plapfigs branch of git@bitbucket.org:pefarrell/fascd.git, in examples/
% $ python3 plap1d.py -p 1.5 -figures -levs 6 -fascd_cycle_type full && mv solution.pdf plap1d1p5.pdf
% $ python3 plap1d.py -p 4.0 -figures -levs 6 -fascd_cycle_type full && mv solution.pdf plap1d4p0.pdf
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{fixfigs/plap1d1p5.pdf} \quad
\includegraphics[width=0.45\textwidth]{fixfigs/plap1d4p0.pdf}
\end{center}
\caption{Solutions $u\ge \psi$ of the $p$-Laplacian VI in Example \ref{ex:results:plap}, for $p=1.5$ (left) and $p=4.0$ (right).}
\label{fig:results:plap}
\end{figure}

% figures in the following visualization were generated using branch elbueler/simplefigs
% of git@bitbucket.org:pefarrell/fascd.git, and the following commands (including imagemagick):
%   cd examples/
%   python3 plap1d.py -fascd_cycle_type multiplicative -mcoarse 4 -levs 3 -figures
%   [save the images into mcd-extended/paper/fixfigs/vcycle/]
%   for X in start2 down2 down1 up0 up1 up2 next2; do mogrify -trim $X.png $X.png; done
\begin{figure}[ht]
\begin{center}
\input{tikz/imagesvcycle.tex}
\end{center}
\caption{Visualization of one FASCD V-cycle iteration for Example \ref{ex:results:plap}, with $p=1.5$, $J=3$, and a coarsest mesh of $m_0=5$ vertices.  Solutions (i.e.~$w^j$, $y^j$, $z^j$) are lines, obstacles ($\underline{\gamma}^j$, $\underline{\phi}^j$, $\underline{\chi}^j$) are strong dots, and the zero function is dotted.  Vertical scale varies.}
\label{fig:imagesvcycle}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py
% and https://github.com/bueler/mcd-extended: paper/results/plap1d.sh|txt
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 3mm}c@{\hskip 3mm}c@{\hskip 4mm}c@{\hskip 5mm}c@{\hskip 6mm}c}
\toprule
\emph{levels} & $m_J$ & V(1,0) & V(0,1) & V(1,1) & F & F$_\eps$ & $\|$error$\|_\infty$ \\
\midrule
 1 &    $7$ &  1 &  1 &  1 &  1 &  1 & $2.3\times 10^{-1}$ \\
 2 &   $13$ &  3 &  3 &  2 &  2 &  1 & $3.3 \times 10^{-2}$ \\
 3 &   $25$ & 12 &  4 &  2 &  1 &  1 & $9.1 \times 10^{-3}$ \\
 4 &   $49$ & NC &  4 &  2 &  1 &  1 & $3.2 \times 10^{-3}$ \\
 5 &   $97$ & NC &  3 &  3 &  1 &  1 & $5.5 \times 10^{-4}$ \\
 6 &  $193$ & NC &  3 &  3 & NC &  1 & $1.7 \times 10^{-4}$ \\
 7 &  $385$ & NC &  3 &  3 &  1 &  1 & $4.7 \times 10^{-5}$ \\
 8 &  $769$ & NC &  4 &  7 &  1 &  1 & $9.5 \times 10^{-6}$ \\
 9 & $1537$ & NC &  5 &  6 & NC &  1 & $3.6 \times 10^{-6}$ \\
10 & $3073$ & NC & 11 & 19 &  1 &  1 & $4.9 \times 10^{-7}$ \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for V- and F-cycles on the $p=1.5$ problem in Example \ref{ex:results:plap}.  NC $=$ did not converge after 50 iterations.  See text regarding F$_\eps$ and error.}
\label{tab:results:fastplap1d}
\end{table}

% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py
% and https://github.com/bueler/mcd-extended: paper/results/plap1d.sh|txt
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c@{\hskip 4mm}c@{\hskip 6mm}c}
\toprule
\emph{levels} & $m_J$ & V & V$_4$ & F & $\|$error$\|_\infty$ \\
\midrule
 1 &    $7$ &  1 &  1 &  1 & $8.7 \times 10^{-2}$ \\
 2 &   $13$ &  1 &  1 &  1 & $3.8 \times 10^{-2}$ \\
 3 &   $25$ &  2 &  1 &  1 & $1.6 \times 10^{-2}$ \\
 4 &   $49$ &  4 &  2 &  1 & $6.3 \times 10^{-3}$ \\
 5 &   $97$ & NC &  2 &  1 & $2.3 \times 10^{-3}$ \\
 6 &  $193$ & NC &  1 &  1 & $7.0 \times 10^{-4}$ \\
 7 &  $385$ & NC &  2 &  1 & $2.0 \times 10^{-4}$ \\
 8 &  $769$ & NC &  2 &  1 & $1.1 \times 10^{-4}$ \\
 9 & $1537$ & NC &  2 &  1 & $4.0 \times 10^{-5}$ \\
10 & $3073$ & NC &  2 &  1 & $1.5 \times 10^{-5}$ \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for V- and F-cycles on the $p=4.0$ problem in Example \ref{ex:results:plap}.  See text regarding V$_4$ and error.}
\label{tab:results:degenerateplap1d}
\end{table}

@@

% REGENERATE using git@bitbucket.org:pefarrell/fascd.git, in examples/
%   mpiexec -n 16 --map-by core --bind-to hwthread python3 pollutant.py -dim 2 -levs 7 -o poll2d.pvd
%   paraview poll2d.pvd
% to plot coincidence sets use ranges 0 <= u <= 0.00001 and 0.99999 <= u <= 1 and
% preset "xray" and invert colors (for u=0) or keep colors (u=1)
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.35\textwidth]{fixfigs/poll2d-zero-set.png} \qquad \includegraphics[width=0.35\textwidth]{fixfigs/poll2d-one-set.png}
\end{center}
\caption{Coincidence sets for the 2D bi-obstacle problem in Example \ref{ex:results:advdiff}: $u=0$ (left) and $u=1$ (right).}
\label{fig:results:advdiff}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/pollutant.py
% and https://github.com/bueler/mcd-extended: paper/results/pollutant.sh|txt
\begin{table}[ht]
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
\emph{levels} & $m_J$ & $d=2$ & $d=3$ \\
\midrule
 1 &    $16^d$ & 1 & 1 \\
 2 &    $31^d$ & 2 & 2 \\
 3 &    $61^d$ & 2 & 2 \\
 4 &   $121^d$ & 2 & 2 \\
 5 &   $241^d$ & 2 & 3 \\
 6 &   $481^d$ & 2 \\
 7 &   $961^d$ & 3 \\
 8 &  $1921^d$ & 3 \\
 9 &  $3841^d$ & 3 \\
\bottomrule
\end{tabular}
\bigskip
\caption{F-cycle iterations for 2D ($P_1$, serial) and 3D ($Q_1$, 16 processes) solutions of the advection-diffusion bi-obstacle VI problem in Example \ref{ex:results:advdiff}.}
\label{tab:results:advdiff}
\end{table}

@@

% to regenerate from git@bitbucket.org:pefarrell/fascd.git: examples/:
%   $ mpiexec -n 16 --map-by core --bind-to hwthread python3 sia.py -levs 8 -bumps \
%       -mcoarse 8 -fascd_cycle_type full -fascd_monitor -fascd_rtol 2.0e-4 \
%       -fascd_atol 1.0e-8 -o sialev8.pvd
\begin{figure}[ht]
\begin{center}
\includegraphics[width=1.0\textwidth]{fixfigs/sialev8scene.png}
\end{center}
\caption{Solution of Example \ref{ex:sia} over a bumpy bedrock topography (grey), with the ice speed as surface coloring and 100-times vertical exaggeration.}
\label{fig:results:siascene}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/sia.py
% and https://github.com/bueler/mcd-extended: paper/results/siaweak.sh|txt
\begin{table}[ht]
\begin{tabular}{c@{\hskip 4mm}c@{\hskip 4mm}c@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
$P$ & \emph{levels} & $m_J$ & \emph{F-cycles} & \emph{time} (s) \\
\midrule
 1 & 6 & $641^2$ & 3 & 98 \\
 4 & 7 & $1281^2$ & 3 & 98 \\
 16 & 8 & $2561^2$ & 3 & 124 \\
 64 & 9 & $5121^2$ & 3 & 136 \\
 256 & 10 & $10241^2$ & 2 & 95 \\
 1024 & 11 & $20481^2$ & 2 & 177 \\
 \bottomrule
\end{tabular}
\bigskip
\caption{Iterations and run time (wall clock, in seconds) for parallel FASCD F-cycle solutions of Example \ref{ex:sia} on $P$ processes.}
\label{tab:results:siaweak}
\end{table}
\end{example}

@@

\elb{acknowledge Lawrence for help with monotone injections?}

>>>>

\title{A full approximation scheme multilevel method \\ for nonlinear variational inequalities\thanks{Submitted to the editors DATE.
\funding{EB was supported by a Faculty Development Travel Award from United Academics, University of Alaska Fairbanks. PEF was supported by the Engineering and Physical Sciences Research Council [EPSRC grants EP/R029423/1 and EP/W026163/1]. This work used the ARCHER2 UK National Supercomputing Service (https://www.archer2.ac.uk). PEF thanks Lawrence Mitchell for advice on the implementation of FASCD, and thanks Jack D.~Betteridge for assistance with the numerical experiments of Example \ref{ex:results:sia}.}}}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{genfigs/cartoon.pdf}
\caption{A constraint decomposition (CD) for a unilateral obstacle problem on a two-point space $\Omega=\{x_1,x_2\}$, with $\mathcal{V}=\left\{v \,:\, \Omega \to \RR\right\}$ and $\mathcal{K}=\{v\ge \psi\}$.}
\label{fig:cartoon}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{llc}
\toprule
\emph{name}  & \emph{action}  & \emph{linear?} \\ \midrule
canonical prolongation        & $P:\mathcal{V}^{j-1}\to\mathcal{V}^j$ & \,\checkmark \\
canonical (dual) restriction  & $R:(\mathcal{V}^j)'\to(\mathcal{V}^{j-1})'$ & \,\checkmark \\
(nodal) injection             & $\iR:\mathcal{V}^j\to\mathcal{V}^{j-1}$ & \,\checkmark \\
maximum injection           & $\maxR:\tilde{\mathcal{V}}^j\to\tilde{\mathcal{V}}^{j-1}$ & \ding{55} \\
minimum injection           & $\minR:\tilde{\mathcal{V}}^j\to\tilde{\mathcal{V}}^{j-1}$ & \ding{55} \\
\bottomrule
\end{tabular}
\caption{Transfer operators used in this paper.}
\label{tab:transfers}
\end{table}

@@

\begin{figure}[ht]
\centering
\input{tikz/Rplusminus.tex}
\caption{The monotone injection operators $\maxR$ and $\minR$ assign to a coarse degree of freedom (blue) the maximum and minimum respectively of the fine function over the patch of coarse cells sharing its vertex. The coarse mesh is in black and the fine in grey.}
\label{fig:Rplusminus}
\end{figure}

@@

\begin{figure}[ht]
\centering
\begin{tabular}{cc}
\input{tikz/directRbadfine.tex}
&
\input{tikz/directRbadcoarse.tex}
\end{tabular}
\caption{For the finer-level constraints $\underline{\gamma}^1$ (blue) and $\overline{\gamma}^1$ (red) on the left, direct application of $\iR,\minR,\maxR$ is problematic.  For example, if we apply the monotone injections then the resulting coarser-level constraint set $\mathcal{K}^0$ is empty because $\maxR \underline{\gamma}^1 > \minR \overline{\gamma}^1$ (right).  Defect constraints avoid this difficulty.}
\label{fig:directRbad}
\end{figure}

@@

%REGENERATE using https://github.com/bueler/mg-glaciers:
%$ cd mg-glaciers/py/
%$ [modify decomposition() inside visualize.py to turn off axes and print \gamma for obstacle]
%$ ./obstacle.py -J 5 -jcoarse 1 -random -randommodes 8 -diagnostics -o defect.pdf
%fine level 5 (m=63): using 20 V(1,0) cycles -> 38.750 WU
\begin{figure}[ht]
\centering
\includegraphics[width=0.65\textwidth]{fixfigs/chiphilevels.pdf}
\caption{Unilateral LDCs $\underline{\chi}^j$ are generated from $\underline{\chi}^J = \underline{\gamma}^J - w^J$ using maximum injection: $\underline{\chi}^j = \maxR \underline{\chi}^{j+1}$.}
\label{fig:chiphilevels}
\end{figure}

@@

\begin{figure}[ht]
\centering
\input{tikz/vcycle.tex}
\caption{The FASCD V-cycle computes downward corrections $y_j \in \mathcal{D}^j$, but the upward corrections $z_j\in\mathcal{U}^j$ are in larger sets.}
\label{fig:fascdvcycle}
\end{figure}

@@

\begin{figure}[h]
\centering
\input{tikz/fcycle.tex}
\caption{F-cycle Algorithm \ref{alg:fascd-fcycle} initially restricts and injects the data $\ell^J,\underline{\gamma}^J,\overline{\gamma}^J$ down to level $j=0$ (gray).  Then it prolongs and truncates (doubled edges) to create an admissible initial iterate on the next-finer level.  Solution on each level is by V-cycles. See Figure \ref{fig:fascdvcycle} for the other symbols.}
\label{fig:fcycle}
\end{figure}

@@

%REGENERATE using git@bitbucket.org:pefarrell/fascd.git, in examples/
%$ python3 drape.py -prob ball -levs 9 -o ball -fascd_rtol 1.0e-6 -fascd_atol 1.0e-6 -fascd_cycle_type full
%$ mpiexec -n 16 python3 drape.py -prob spiral -levs 10 -o spiral.pvd -fascd_levels_snes_converged_reason -fascd_rtol 1.0e-6 -fascd_atol 1.0e-6 -fascd_cycle_type full
%$ paraview ball|spiral.pvd
%use preset "xray" and invert colors; for spiral.pvd, show lgap = u - lb as black if above 0.02; for ball i used 0.001
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{fixfigs/ball-set.png} \qquad \includegraphics[width=0.35\textwidth]{fixfigs/spiral-set.png}
\caption{Coincidence sets for the ball and spiral problems in Example \ref{ex:results:classical}.}
\label{fig:results:classical}
\end{figure}

% see git@bitbucket.org:pefarrell/fascd.git: examples/drape.py
% and https://github.com/bueler/mcd-extended: paper/results/drape.sh|txt
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}cccccc}
\toprule
\multirow{2}{*}{\emph{levels}} & \multirow{2}{*}{$m_J$} & \multicolumn{3}{c}{\,\emph{ball}} & \multicolumn{3}{c}{\,\emph{spiral}} \\ \cmidrule(lr){3-5} \cmidrule(lr){6-8}
   &          & V-cycle & F-cycle & RS only & V-cycle & F-cycle & RS only \\
\midrule
 1 &    $5^2$ &  1 &  1 &  1  &  1 &  1 &  1 \\
 2 &    $9^2$ &  2 &  1 &  2  &  2 &  1 &  2 \\
 3 &   $17^2$ &  2 &  2 &  3  &  3 &  2 &  4 \\
 4 &   $33^2$ &  3 &  2 &  6  &  3 &  2 &  7 \\
 5 &   $65^2$ &  3 &  2 &  8  &  4 &  3 &  9 \\
 6 &  $129^2$ &  4 &  2 & 17  &  4 &  3 & 16 \\
 7 &  $257^2$ &  4 &  2 & 33  &  4 &  3 & 27 \\
 8 &  $513^2$ &  5 &  2 & 65  &  5 &  3 & 48 \\
 9 & $1025^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
10 & $2049^2$ &  5 &  2 & \XX &  5 &  3 & \XX \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for FASCD V-cycle and F-cycle algorithms in Example \ref{ex:results:classical}.  Smoother-only runs marked \XX\xspace were not attempted.}
\label{tab:results:classical}
\end{table}

@@

%REGENERATE using elbueler/plapfigs branch of git@bitbucket.org:pefarrell/fascd.git, in examples/
% $ python3 plap1d.py -p 1.5 -figures -levs 6 -fascd_cycle_type full && mv solution.pdf plap1d1p5.pdf
% $ python3 plap1d.py -p 4.0 -figures -levs 6 -fascd_cycle_type full && mv solution.pdf plap1d4p0.pdf
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{fixfigs/plap1d1p5.pdf} \quad
\includegraphics[width=0.45\textwidth]{fixfigs/plap1d4p0.pdf}
\caption{Solutions $u\ge \psi$ of the $p$-Laplacian VI in Example \ref{ex:results:plap}, for $p=1.5$ (left) and $p=4.0$ (right).}
\label{fig:results:plap}
\end{figure}

% figures in the following visualization were generated using branch elbueler/simplefigs
% of git@bitbucket.org:pefarrell/fascd.git, and the following commands (including imagemagick):
%   cd examples/
%   python3 plap1d.py -fascd_cycle_type multiplicative -mcoarse 4 -levs 3 -figures
%   [save the images into mcd-extended/paper/fixfigs/vcycle/]
%   for X in start2 down2 down1 up0 up1 up2 next2; do mogrify -trim $X.png $X.png; done
\begin{figure}[ht]
\centering
\input{tikz/imagesvcycle.tex}
\caption{Visualization of one FASCD V-cycle iteration for Example \ref{ex:results:plap}, with $p=1.5$, $J=3$, and a coarsest mesh of $m_0=5$ vertices.  Solutions (i.e.~$w^j$, $y^j$, $z^j$) are lines, obstacles ($\underline{\gamma}^j$, $\underline{\phi}^j$, $\underline{\chi}^j$) are strong dots, and the zero function is dotted.  Vertical scale varies.}
\label{fig:imagesvcycle}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py
% and https://github.com/bueler/mcd-extended: paper/results/plap1d.sh|txt
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 3mm}c@{\hskip 3mm}c@{\hskip 4mm}c@{\hskip 5mm}c@{\hskip 6mm}c}
\toprule
\emph{levels} & $m_J$ & V(1,0) & V(0,1) & V(1,1) & F & F$_\eps$ & $\|$error$\|_\infty$ \\
\midrule
 1 &    $7$ &  1 &  1 &  1 &  1 &  1 & $2.3\times 10^{-1}$ \\
 2 &   $13$ &  3 &  3 &  2 &  2 &  1 & $3.3 \times 10^{-2}$ \\
 3 &   $25$ & 12 &  4 &  2 &  1 &  1 & $9.1 \times 10^{-3}$ \\
 4 &   $49$ & NC &  4 &  2 &  1 &  1 & $3.2 \times 10^{-3}$ \\
 5 &   $97$ & NC &  3 &  3 &  1 &  1 & $5.5 \times 10^{-4}$ \\
 6 &  $193$ & NC &  3 &  3 & NC &  1 & $1.7 \times 10^{-4}$ \\
 7 &  $385$ & NC &  3 &  3 &  1 &  1 & $4.7 \times 10^{-5}$ \\
 8 &  $769$ & NC &  4 &  7 &  1 &  1 & $9.5 \times 10^{-6}$ \\
 9 & $1537$ & NC &  5 &  6 & NC &  1 & $3.6 \times 10^{-6}$ \\
10 & $3073$ & NC & 11 & 19 &  1 &  1 & $4.9 \times 10^{-7}$ \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for V- and F-cycles on the $p=1.5$ problem in Example \ref{ex:results:plap}.  NC $=$ did not converge after 50 iterations.  See text regarding F$_\eps$ and error.}
\label{tab:results:fastplap1d}
\end{table}

% see git@bitbucket.org:pefarrell/fascd.git: examples/plap1d.py
% and https://github.com/bueler/mcd-extended: paper/results/plap1d.sh|txt
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c@{\hskip 4mm}c@{\hskip 6mm}c}
\toprule
\emph{levels} & $m_J$ & V & V$_4$ & F & $\|$error$\|_\infty$ \\
\midrule
 1 &    $7$ &  1 &  1 &  1 & $8.7 \times 10^{-2}$ \\
 2 &   $13$ &  1 &  1 &  1 & $3.8 \times 10^{-2}$ \\
 3 &   $25$ &  2 &  1 &  1 & $1.6 \times 10^{-2}$ \\
 4 &   $49$ &  4 &  2 &  1 & $6.3 \times 10^{-3}$ \\
 5 &   $97$ & NC &  2 &  1 & $2.3 \times 10^{-3}$ \\
 6 &  $193$ & NC &  1 &  1 & $7.0 \times 10^{-4}$ \\
 7 &  $385$ & NC &  2 &  1 & $2.0 \times 10^{-4}$ \\
 8 &  $769$ & NC &  2 &  1 & $1.1 \times 10^{-4}$ \\
 9 & $1537$ & NC &  2 &  1 & $4.0 \times 10^{-5}$ \\
10 & $3073$ & NC &  2 &  1 & $1.5 \times 10^{-5}$ \\
\bottomrule
\end{tabular}
\bigskip
\caption{Iterations for V- and F-cycles on the $p=4.0$ problem in Example \ref{ex:results:plap}.  See text regarding V$_4$ and error.}
\label{tab:results:degenerateplap1d}
\end{table}

@@

% REGENERATE using git@bitbucket.org:pefarrell/fascd.git, in examples/
%   mpiexec -n 16 --map-by core --bind-to hwthread python3 pollutant.py -dim 2 -levs 7 -o poll2d.pvd
%   paraview poll2d.pvd
% to plot coincidence sets use ranges 0 <= u <= 0.00001 and 0.99999 <= u <= 1 and
% preset "xray" and invert colors (for u=0) or keep colors (u=1)
\begin{figure}[ht]
\centering
\includegraphics[width=0.35\textwidth]{fixfigs/poll2d-zero-set.png} \qquad \includegraphics[width=0.35\textwidth]{fixfigs/poll2d-one-set.png}
\caption{Coincidence sets for the 2D bi-obstacle problem in Example \ref{ex:results:advdiff}: $u=0$ (left) and $u=1$ (right).}
\label{fig:results:advdiff}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/pollutant.py
% and https://github.com/bueler/mcd-extended: paper/results/pollutant.sh|txt
\begin{table}[ht]
\centering
\begin{tabular}{lr@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
\emph{levels} & $m_J$ & $d=2$ & $d=3$ \\
\midrule
 1 &    $16^d$ & 1 & 1 \\
 2 &    $31^d$ & 2 & 2 \\
 3 &    $61^d$ & 2 & 2 \\
 4 &   $121^d$ & 2 & 2 \\
 5 &   $241^d$ & 2 & 3 \\
 6 &   $481^d$ & 2 \\
 7 &   $961^d$ & 3 \\
 8 &  $1921^d$ & 3 \\
 9 &  $3841^d$ & 3 \\
\bottomrule
\end{tabular}
\bigskip
\caption{F-cycle iterations for 2D ($P_1$, serial) and 3D ($Q_1$, 16 processes) solutions of the advection-diffusion bi-obstacle VI problem in Example \ref{ex:results:advdiff}.}
\label{tab:results:advdiff}
\end{table}

@@

% to regenerate from git@bitbucket.org:pefarrell/fascd.git: examples/:
%   $ mpiexec -n 16 --map-by core --bind-to hwthread python3 sia.py -levs 8 -bumps \
%       -mcoarse 8 -fascd_cycle_type full -fascd_monitor -fascd_rtol 2.0e-4 \
%       -fascd_atol 1.0e-8 -o sialev8.pvd
\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{fixfigs/sialev8scene.png}
\caption{Solution of Example \ref{ex:sia} over a bumpy bedrock topography (grey), with the ice speed as surface coloring and 100-times vertical exaggeration.}
\label{fig:results:siascene}
\end{figure}

@@

% see git@bitbucket.org:pefarrell/fascd.git: examples/sia.py
% and https://github.com/bueler/mcd-extended: paper/results/siaweak.sh|txt
\begin{table}[ht]
\centering
\begin{tabular}{c@{\hskip 4mm}c@{\hskip 4mm}c@{\hskip 7mm}c@{\hskip 4mm}c}
\toprule
$P$ & \emph{levels} & $m_J$ & \emph{F-cycles} & \emph{time} (s) \\
\midrule
 1 & 6 & $641^2$ & 3 & 98 \\
 4 & 7 & $1281^2$ & 3 & 98 \\
 16 & 8 & $2561^2$ & 3 & 124 \\
 64 & 9 & $5121^2$ & 3 & 136 \\
 256 & 10 & $10241^2$ & 2 & 95 \\
 1024 & 11 & $20481^2$ & 2 & 177 \\
 \bottomrule
\end{tabular}
\bigskip
\caption{Iterations and run time (wall clock, in seconds) for parallel FASCD F-cycle solutions of Example \ref{ex:sia} on $P$ processes.}
\label{tab:results:siaweak}
\end{table}
\end{example}

@@
